Racial and Ethnic Differences in ETI

### 2023-08-05 Kamyron Jordan/Racial and Ethnic Differences in ETI/racial_and_ethnic_differences_in_eti.qmd
table formatting

```{r t1}
annual %>%
  select(ReviewYear, race, Hispanicrace) %>%
  tbl_summary(
    by = ReviewYear, missing_text = "Missing",
    statistic = list(all_continuous() ~ "{mean} ({sd})")
  ) %>%
  modify_header(label = paste0("**Year**")) %>%
  bold_labels()
```

@@

```{r t2}
demo %>%
  select(race, Hispanicrace) %>%
  tbl_summary(
    by = Hispanicrace,
    statistic = list(all_continuous() ~ "{mean} ({sd})")
  ) %>%
  modify_header(label = paste0("**", label(annual$Hispanicrace), "**")) %>%
  add_overall() %>%
  bold_labels()
```

@@

```{r t3}
demo %>%
  select(race) %>%
  tbl_summary(statistic = list(all_continuous() ~ "{mean} ({sd})")) %>%
  modify_header(label = paste0("**Race**")) %>%
  bold_labels()
```

@@

```{r t4}
demo %>%
  select(race, Gender, WasGenotyped, F508) %>%
  tbl_summary(
    by = race, missing_text = "Missing",
    statistic = list(all_continuous() ~ "{mean} ({sd})")
  ) %>%
  modify_header(label = paste0("**Race**")) %>%
  add_overall() %>%
  bold_labels()
```

@@

```{r t5}
#| message: false
t5 %>%
  select(
    -eDWID, reviewyear, race, Gender, WasGenotyped, F508, contains("insurance"),
    `Age at Last Visit`, `Mean ppFEV`, `Weight at Last Visit`,
    `Weight %ile at Last Visit`, `BMI at Last Visit`,
    `BMI %ile at Last Visit`
  ) %>%
  tbl_summary(
    by = reviewyear, missing_text = "Missing",
    statistic = list(all_continuous() ~ "{mean} ({sd})")
  ) %>%
  modify_header(label = paste0("**Year**")) %>%
  bold_labels()
```

>>>>

```{r t1}
annual %>%
  select(ReviewYear, race, Hispanicrace) %>%
  tbl_summary(
    by = ReviewYear, missing_text = "Missing",
    statistic = list(all_continuous() ~ "{mean} ({sd})")
  ) %>%
  modify_header(label = paste0("**Year**")) %>%
  bold_labels() %>%
  as_kable_extra()
```

@@

```{r t2}
demo %>%
  select(race, Hispanicrace) %>%
  tbl_summary(
    by = Hispanicrace,
    statistic = list(all_continuous() ~ "{mean} ({sd})")
  ) %>%
  modify_header(label = paste0("**", label(annual$Hispanicrace), "**")) %>%
  add_overall() %>%
  bold_labels() %>%
  as_kable_extra()
```

@@

```{r t3}
demo %>%
  select(race) %>%
  tbl_summary(statistic = list(all_continuous() ~ "{mean} ({sd})")) %>%
  modify_header(label = paste0("**Race**")) %>%
  bold_labels() %>%
  as_kable_extra()
```

@@

```{r t4}
demo %>%
  select(race, Gender, WasGenotyped, F508) %>%
  tbl_summary(
    by = race, missing_text = "Missing",
    statistic = list(all_continuous() ~ "{mean} ({sd})")
  ) %>%
  modify_header(label = paste0("**Race**")) %>%
  add_overall() %>%
  bold_labels() %>%
  as_kable_extra()
```

@@

```{r t5}
#| message: false
t5 %>%
  select(
    -eDWID, reviewyear, race, Gender, WasGenotyped, F508, contains("insurance"),
    `Age at Last Visit`, `Mean ppFEV`, `Weight at Last Visit`,
    `Weight %ile at Last Visit`, `BMI at Last Visit`,
    `BMI %ile at Last Visit`
  ) %>%
  tbl_summary(
    by = reviewyear, missing_text = "Missing",
    statistic = list(all_continuous() ~ "{mean} ({sd})")
  ) %>%
  modify_header(label = paste0("**Year**")) %>%
  bold_labels() %>%
  as_kable_extra()
```
